Analysis of Competence Index

### 2017-05-10 analysis/analysis_competence.Rmd
update

---
title: "Competence distance"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 Feb"
output:  
  md_document:
    variant: markdown_github
---

```{r, warning=FALSE, message=FALSE}}
library("tidyverse")
library("stringr")
```

@@

## Compute competence indexes

@@

```{r}
source(paste0(getwd(), '/script/R/get_coords_trees.R'))

@@

## Plot by site 
```{r}
# Set levels of eleveation 
sj_lowcode  <- paste0('A', str_pad(1:10, 2, pad='0'))
sj_highcode <- paste0('A', 11:20)
ca_lowcode <- c(paste0('B', str_pad(1:10, 2, pad='0')),
            paste0('B', 26:30))
ca_highcode <- paste0('B', 11:25)

@@

# see stackoverflow questions 6862742
gg_circle <- function(radius, xcenter, ycenter, color='black', fill=NA, ...){
  x <- xcenter + radius*cos(seq(0,pi, length.out = 100))
  ymax <- ycenter + radius*sin(seq(0, pi, length.out = 100))
  ymin <- ycenter + radius*sin(seq(0, -pi, length.out = 100))
  annotate("ribbon", x=x, ymin=ymin, ymax=ymax, color=color, fill=fill, ...)
}
```

compete %>%  
  filter(sp != 'Focal') %>%
  ggplot(aes(x=xcord, y=ycord)) + 
  facet_wrap(~id_focal) + 
  geom_point(aes(size=perim_mm), shape=21, fill='transparent') + 
  xlim(-11,11) + ylim(-11,11) + 
  geom_point(aes(x=0, y=0), color='green') +
  theme_bw() +
  gg_circle(radius = 10, xcenter = 0, ycenter = 0) +
  theme(panel.grid.major=element_blank(), 
        panel.grid.minor=element_blank()) 
```

```{r}

```

>>>>

---
title: "Analysis of Competence Index"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 Feb"
output:  
  md_document:
    variant: markdown_github
---

```{r, warning=FALSE, message=FALSE}
library("tidyverse")
library("stringr")
```

@@

## Compute competition indices

The following competition indices were computed: 
### Basal Area

$$\sum_{i=1}^{n}pi\cdot (dbh_{i} / 2)^2$$

@@

```{r}
source(paste0(di, '/script/R/get_coords_trees.R'))

@@

## Plot by site

```{r}
# Set levels of eleveation 
sj_lowcode  <- paste0('A', str_pad(1:10, 2, pad='0'))
sj_highcode <- paste0('A', 11:20)
ca_lowcode <- c(paste0('B', str_pad(1:10, 2, pad='0')),
            paste0('B', 26:30))
ca_highcode <- paste0('B', 11:25)

@@

#### San Juan 
```{r, echo=FALSE}
# see stackoverflow questions 6862742
gg_circle <- function(radius, xcenter, ycenter, color='black', fill=NA, ...){
  x <- xcenter + radius*cos(seq(0,pi, length.out = 100))
  ymax <- ycenter + radius*sin(seq(0, pi, length.out = 100))
  ymin <- ycenter + radius*sin(seq(0, -pi, length.out = 100))
  annotate("ribbon", x=x, ymin=ymin, ymax=ymax, color=color, fill=fill, ...)
}

compete %>%  
  filter(sp != 'Focal') %>%
  filter(loc == 'SJ') %>% 
  ggplot(aes(x=xcord, y=ycord)) + 
  facet_wrap(~id_focal) + 
  geom_point(aes(size=dn), shape=21, fill='transparent') +
  xlim(-11,11) + ylim(-11,11) + 
  geom_point(aes(x=0, y=0), color='green') +
  theme_bw() +
  gg_circle(radius = 10, xcenter = 0, ycenter = 0) +
  theme(panel.grid.major=element_blank(), 
        panel.grid.minor=element_blank(), 
        strip.background = element_rect(colour = "black", fill ='transparent')) 
```

#### Canar 
```{r, echo=FALSE, fig.height=8, fig.width=12}
compete %>%  
  filter(sp != 'Focal') %>%
  filter(loc == 'CA') %>% 
  ggplot(aes(x=xcord, y=ycord)) + 
  facet_wrap(~id_focal) + 
  geom_point(aes(size=dn), shape=21, fill='transparent') +
  xlim(-11,11) + ylim(-11,11) + 
  geom_point(aes(x=0, y=0), color='green') +
  theme_bw() +
  gg_circle(radius = 10, xcenter = 0, ycenter = 0) +
  theme(panel.grid.major=element_blank(), 
        panel.grid.minor=element_blank(), 
        strip.background = element_rect(colour = "black", fill ='transparent')) 
```
